---
title: "predictions"
author: "Michael Fedell"
date: "12/1/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source('./LinearModel/linear-model.R', chdir = T)
source('./LogisticModel/logistic-model.R', chdir = T)
```

# Model Results

The logistic regression and mulitple linear regression models willbe combined together to come up with a predicted response for each customer in the test set.

This will be done by first predicting the customer's liklihood to respond to the promotion via the logistic regression model. After determining response liklihood, the mulitple linear regression will be applied to predict how _much_ a customer will purchase after the promotion.

In summary: E(logtargamt) = P(logtargamt > 0) * E(logtargamt | logtargamt > 0)

## Logistic Regression

The logisitc model was developed by fitting a binomial generalized linear model to the test data set using a collection of predictors both natural and engineered. The predictors used in the final model are as follows:

- avgNetOrder
- sumQty
- recency
- frequency
- tof
- oneMonth
- threeMonth
- oneYear
- sumQtyPerTof


## Multiple Regression

The mulitple linear regression was produced by several iterations of feature engineering and model variation. Ultimately, a best model was obtained via stepwise regression allowed to move in both forward and backward directions. The final predictors used are as follows:

- recency
- frequency
- amount
- amountPer
- sumQty
- oneMonth


## Synthesis

These two models will be brought together to form predictions on the expected amount purchased for customers in the test set.

We will narrow down the full test data to just the needed variables, while also filtering out several of the significant outliers (with more than 1000 orders)

```{r}
predictions <- test.full %>%
  select(avgNetOrder, sumQty, recency, frequency, tof, amount,
         amountPer, oneMonth, threeMonth, oneYear, sumQtyPerTof,
         logtargamt) %>% filter(tof > 0, sumQty < 1000)
```

The predictions given by the logistic regression are biased towards responders becuase the training data was oversampled to better balance responses. This bias will be corrected below

```{r}
p2 <- predict(log.best, newdata = predictions, type = 'response')
m <- nrow(filter(train.rebalanced, respond == 1)) / nrow(train.rebalanced) / .0393
p1 <- exp(-log(m) + log(p2 / (1 - p2)))/(1 + exp(-log(m) + log(p2 / (1 - p2))))

predictions$probRespond <- p1
```

The multiple regression can now be applied to the set to predict the amount purchased. These predictions will be scaled by the customer's liklihood to respond to offer (as calculated by logistic regression).

```{r}
predictions$predLogtargamt <- predict(ml.best, newdata = predictions)
predictions$scaledLogtargamt <- predictions$probRespond * predictions$predLogtargamt
```

The predicted logtargamts must now be transformed back to a normal, predicted amount in Euros by performing the inverse of the original log transformation ($ln(amt + 1)$)

```{r}
predictions$predTargamt <- exp(predictions$scaledLogtargamt) - 1
predictions$targamt <- exp(predictions$logtargamt) - 1
```

```{r}
SSEP <- sum((predictions$predTargamt - predictions$targamt)^2); SSEP
```

