---
title: "mf-eda"
author: "Michael Fedell"
date: "11/13/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
```

# Exploratory Data Analysis

```{r}
source('../loader.R', chdir = T)

summary(book[2:6])
```


```{r}
for (i in names(book[2:6])) {
  hist(book[[i]], xlab = i)
}
```

Most of the data is extrememly long-tailed, also, amount has an **extreme** outlier at some $500,000. This should likely be excluded from the data.

Similarly, removing the zero-value entries may help to visualize the dispersion of data.


```{r}
hist(book$logtargamt[book$logtargamt > 0])
par(mfrow = c(1, 3))
boxplot(book$recency, xlab = 'Recency')
boxplot(book$frequency, outline = F, xlab = 'Frequency')
boxplot(book$amount[book$amount < 1000], xlab = 'Amount')
par(mfrow = c(1, 1))
```

Lots of high outliers in Frequency so they have been omitted from the boxplot


```{r}
plot(book[2:6])
```

Not super helpful...

```{r}
orders$net <- orders$qty * orders$price
hist(orders$net[orders$net < 50])
```


Let's take a look at the orders of customers who responded positively (logtargamt > 0)

```{r}
orders.responsder <- book.train %>% 
  filter(logtargamt > 0) %>%
  merge(orders, by = 'id')
summary(orders.responsder)
```


```{r}
plot(orders.responsder[c(2, 6, 8)])
```

Let's look at the recency, frequency, and avgNetOrder for each customer

```{r}
book.train.full <- orders %>% 
  group_by(id) %>% 
  summarise(avgNetOrder = mean(net)) %>%
  merge(book.train.merge, by = 'id')
book.train.full %>% 
  select(logtargamt, recency, frequency, avgNetOrder, tof) %>% plot()
```
